Post-Disturbance Tree Community Trajectories in a Neotropical Forest

### 2018-06-28 WholePlotTrajectories.Rmd
new graphs

keywords: [Taxonomic and Functional Biodiversity, Neotropical Forests, Disturbance Trajectories, Intermediate Disturbance Hypothesis, Long-term Resilience]
journalinfo: Hal xxx
archive: DOI xxxx
date: "`r format(Sys.time(), '%d %B %Y')`"
preamble: >
  \usepackage{textcomp}
  \DeclareUnicodeCharacter{B0}{\textdegree}
  \usepackage{tabu}
  \usepackage{caption}
  \captionsetup{justification = justified}
  \renewenvironment{table}{\begin{table*}}{\end{table*}\ignorespacesafterend}
  \hyphenation{bio-di-ver-si-ty sap-lings re-or-gan-i-za-tion}
bibliography: references.bib
lang: english
keywordlabel: Keywords
corrauthorlabel: Corresponding author
output:
  bookdown::pdf_book:
    base_format: EcoFoG::article
    keep_tex: TRUE
  bookdown::gitbook: default
  bookdown::word_document2: default
---

@@

To counter taxonomic uncertainties due to the variability of botanical identification levels (in space) and protocols (in time), the taxonomic composition and diversity analysis were conducted at the genus level, *i.e.* referring to the genus of observed or trialed botanical names.
Trajectories of communities taxonomic and functional variations in composition after disturbance were followed in a two-dimensional NMDS ordination space of the 30 years monitored.
Two NMDS were conducted to map either taxonomic flora inventories or communities functional composition based on the 7 leaf, stem and life history traits (without seed mass classes).
In both cases the NMDS were performed using occurrence-based (Jaccard) and abundance-based (Bray-Curtis) dissimilarity measures. 
Trajectories along time in the plan were reported through the euclidean distance of successive inventories to the reference inventories in 1989, *i.e.* 2-3 years after disturbance, when the uncertainty degree did not exceed 30% of undetermined trees. 
To compensate the intrinsinc difference among plots, the trajectories corresponded to the euclidean differences along time with the reference inventory in 1989.
Univariate trajectories of the leaf, stem and life-history traits were also visualized with the community weighted means (CWM) [@Diaz2007;@Garnier2004]. 
Species seed mass corresponded to 5 classes of increasing mass, seed mass trajectories were therefore reported as the proportion of each class in the inventories.

@@

```{r NMDSplans, out.width = '100%', echo=FALSE, fig.cap="Plot trajectories in terms of flora composition (left panels (ref:Bolda) and (ref:Boldc)) and functional composition (right panels (ref:Boldb) and (ref:Boldd)) in a two-dimensional NMDS space. Lower panels ((ref:Boldc) and (ref:Boldd)) represent the euclidean distance to initial condition along the 30 sampled years. Colors are treatments: green (control), blue (T1), orange (T2), red (T3) with shaded areas the credibility intervals", fig.env="figure*"}
load("DB/FunctionalComposition_forGraphs");load("DB/TaxoComposition_forGraphs")
load("DB/FunctionalComposition_forGraphs");load("DB/TaxoComposition_forGraphs")

par(mfrow=c(2,2))
TaxoCompo(MatrepTaxo)
FunCompo(MatrepFun)
TaxoDist(MatrepTaxo)
FunDist(MatrepFun)

>>>>

keywords: [Taxonomic and Functional Biodiversity, Neotropical Forests, Disturbance Trajectories, Intermediate Disturbance Hypothesis, Long-term Resilience]
journalinfo: Hal xxx
archive: DOI xxxx
date: "`r format(Sys.time(), '%d %B %Y')`"
preamble: >
  \usepackage{textcomp}
  \DeclareUnicodeCharacter{B0}{\textdegree}
  \usepackage{tabu}
  \usepackage{caption}
  \captionsetup{justification = justified}
  \renewenvironment{table}{\begin{table*}}{\end{table*}\ignorespacesafterend}
  \hyphenation{bio-di-ver-si-ty sap-lings re-or-gan-i-za-tion}
bibliography: references.bib
lang: english
keywordlabel: Keywords
corrauthorlabel: Corresponding author
output:
  bookdown::gitbook: default
  bookdown::pdf_book:
    base_format: EcoFoG::article
    keep_tex: TRUE
  bookdown::word_document2: default
---

@@

To counter taxonomic uncertainties due to the variability of botanical identification levels (in space) and protocols (in time), the taxonomic composition and diversity analysis were conducted at the genus level, *i.e.* referring to the genus of observed or trialed botanical names.
Trajectories of communities taxonomic and functional variations in composition after disturbance were followed in a two-dimensional NMDS ordination space of the 30 years monitored.
Two NMDS were conducted to map either taxonomic flora inventories or communities functional composition based on the 7 leaf, stem and life history traits (without seed mass classes).
In both cases the NMDS were performed using abundance-based (Bray-Curtis) dissimilarity measures. 
Trajectories along time were reported through the distance between successive inventories and the reference inventories in 1989, *i.e.* 2-3 years after disturbance, when the uncertainty degree did not exceed 30% of undetermined trees. 
Taxonomic trajectories were measured through the euclidean distance between inventories in the multivariate space of all inventories species.
Functional trajectories were measured through the sum of euclidean distances among traits density distributions between inventories.
To compensate the intrinsinc difference among plots, the trajectories corresponded to the euclidean differences along time with the reference inventory in 1989.
Univariate trajectories of the leaf, stem and life-history traits were also visualized with the community weighted means (CWM) [@Diaz2007;@Garnier2004]. 
Species seed mass corresponded to 5 classes of increasing mass, seed mass trajectories were therefore reported as the proportion of each class in the inventories.

@@

```{r NMDSplans, out.width = '100%', echo=FALSE, fig.cap="Plot trajectories in terms of flora composition (left panels (ref:Bolda) and (ref:Boldc)) and functional composition (right panels (ref:Boldb) and (ref:Boldd)) in a two-dimensional NMDS space. Lower panels ((ref:Boldc) and (ref:Boldd)) represent the euclidean distance to initial condition along the 30 sampled years. Colors are treatments: green (control), blue (T1), orange (T2), red (T3) with shaded areas the credibility intervals", fig.env="figure*"}
load("DB/FunctionalComposition_forGraphs");load("DB/TaxoComposition_forGraphs")
load("DB/FunDistance_ForGraphs");load("DB/TaxoDistance_ForGraphs")

par(mfrow=c(2,2))
TaxoCompo(MatrepTaxo)
FunCompo(MatrepFun)
EuclidDist(TaxoEuclid)
EuclidDist(FunEuclid)

### 2018-06-28 WholePlotTrajectories.tex
new graphs

To counter taxonomic uncertainties due to the variability of botanical
identification levels (in space) and protocols (in time), the taxonomic
composition and diversity analysis were conducted at the genus level,
\emph{i.e.} referring to the genus of observed or trialed botanical
names. Trajectories of communities taxonomic and functional variations
in composition after disturbance were followed in a two-dimensional NMDS
ordination space of the 30 years monitored. Two NMDS were conducted to
map either taxonomic flora inventories or communities functional
composition based on the 7 leaf, stem and life history traits (without
seed mass classes). In both cases the NMDS were performed using
occurrence-based (Jaccard) and abundance-based (Bray-Curtis)
dissimilarity measures. Trajectories along time in the plan were
reported through the euclidean distance of successive inventories to the
reference inventories in 1989, \emph{i.e.} 2-3 years after disturbance,
when the uncertainty degree did not exceed 30\% of undetermined trees.
To compensate the intrinsinc difference among plots, the trajectories
corresponded to the euclidean differences along time with the reference
inventory in 1989. Univariate trajectories of the leaf, stem and
life-history traits were also visualized with the community weighted
means (CWM) \citep{Diaz2007, Garnier2004}. Species seed mass
corresponded to 5 classes of increasing mass, seed mass trajectories
were therefore reported as the proportion of each class in the
inventories.

>>>>

To counter taxonomic uncertainties due to the variability of botanical
identification levels (in space) and protocols (in time), the taxonomic
composition and diversity analysis were conducted at the genus level,
\emph{i.e.} referring to the genus of observed or trialed botanical
names. Trajectories of communities taxonomic and functional variations
in composition after disturbance were followed in a two-dimensional NMDS
ordination space of the 30 years monitored. Two NMDS were conducted to
map either taxonomic flora inventories or communities functional
composition based on the 7 leaf, stem and life history traits (without
seed mass classes). In both cases the NMDS were performed using
abundance-based (Bray-Curtis) dissimilarity measures. Trajectories along
time were reported through the distance between successive inventories
and the reference inventories in 1989, \emph{i.e.} 2-3 years after
disturbance, when the uncertainty degree did not exceed 30\% of
undetermined trees. Taxonomic trajectories were measured through the
euclidean distance between inventories in the multivariate space of all
inventories species. Functional trajectories were measured through the
sum of euclidean distances among traits density distributions between
inventories. To compensate the intrinsinc difference among plots, the
trajectories corresponded to the euclidean differences along time with
the reference inventory in 1989. Univariate trajectories of the leaf,
stem and life-history traits were also visualized with the community
weighted means (CWM) \citep{Diaz2007, Garnier2004}. Species seed mass
corresponded to 5 classes of increasing mass, seed mass trajectories
were therefore reported as the proportion of each class in the
inventories.
